{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-10-10 paper/tex/sections/results.tex
fix explanation of NSNS no high ecc systems

\paragraph{Eccentricity} In Fig.~\ref{fig:fiducial_pdf_distributions}d we show the eccentricity distributions. We find that most systems (73\%) will have eccentricities larger than $0.01$ during the LISA mission, which should in principle be detectable according to \citet{Nishizawa+2016}. This means that we will potentially be able to use eccentricity to distinguish these sources from WD sources (see Sec.~\ref{sec:WDWD_distinguish}). We note that several previous studies assumed all systems to be circular when calculating the detection rates \citep[e.g.][]{Liu+2014, Lamberts+2018, Sesana+2020}. 
See Sec.~\ref{sec:compare_studies} for a discussion of the impact of this assumption

@@

The lower abundance of highly eccentric systems among the NSNS and BHNS systems may seem counter-intuitive since neutron stars receive stronger natal kicks, which one may expect to lead to more eccentric systems.  However, in practice, these stronger kicks often disrupt these systems.

\todo{@Selma suggests we return to this section. NSs do \textbf{NOT} receive stronger natal kicks in our simulations since most are formed through ECSN e.g. and have 30km/s instead of 265km/s. }

>>>>

\paragraph{Eccentricity} In Fig.~\ref{fig:fiducial_pdf_distributions}d we show the eccentricity distributions. We find that most systems (73\%) will have eccentricities larger than $0.01$ during the LISA mission, which should in principle be detectable according to \citet{Nishizawa+2016}. This means that we will potentially be able to use eccentricity to distinguish these sources from WD sources (see Sec.~\ref{sec:WDWD_distinguish}). We note that several previous studies assumed all systems to be circular when calculating the detection rates \citep[e.g.][]{Liu+2014, Lamberts+2018, Sesana+2020}. See Sec.~\ref{sec:compare_studies} for a discussion of the impact of this assumption.

@@

The lower abundance of highly eccentric systems among the NSNS and BHNS systems may seem counter-intuitive since neutron stars are lower mass and would be more strongly affected by natal kicks, which one may expect to lead to more eccentric systems. However, the majority of NSs in our simulations are formed through ECSN and USSN and for these types of supernovae we draw from a Maxwellian with $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$. Thus the kicks received by NSs in our simulations are often much smaller than for BHs.
